Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-13 robdml.tex
pp1

{\bf{Previous works \cite{} imply that an appropriate adversary for the inner
\emph{maximization} problem should increase the loss to an ``intermediate''
point between that of benign examples (\ie, unperturbed examples) and the
theoretical upper bound.}}
%
In this paper, we argue such point can be reached by a direct and efficient
adversary.
%
Besides, we conjecture the triplet sampling strategy has a key impact in
adversarial training, because it is also able to greatly influence the
mathematical expectation of loss even without adversarial attack.

>>>>

Inspired by previous works~\cite{advrank,robrank}, we conjecture that an
appropriate adversary for the inner \emph{maximization} problem should
increase the loss to an ``intermediate''
point between that of benign examples (\ie, unperturbed examples) and the
theoretical upper bound.
%
Such point should be reached by an efficient adversary directly.
%
Besides, we speculate the triplet sampling strategy has a key impact in
adversarial training, because it is also able to greatly influence the
mathematical expectation of loss even without adversarial attack.
